AI Safety for High Energy Physics

### 2019-08-02 documentation/manuscript.tex
added D2 attack

To illustrate, introduce example and simulation, ...

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.23\textwidth]{figures/panel_1.pdf}
\includegraphics[width=0.23\textwidth]{figures/panel_2.pdf}
\includegraphics[width=0.23\textwidth]{figures/panel_3.pdf}
\includegraphics[width=0.2\textwidth]{figures/NN_FGSM.pdf}
\label{fig:FGSM}
\caption{Individual jet adversary.}
\end{figure}

>>>>

To illustrate, introduce example and simulation, ...  The dataset~\cite{gregor_kasieczka_2019_2629073} includes generic quark and gluon scattering as the background process and boosted new particles decaying into jets as the signal process. Pythia~8~\cite{Sjostrand:2006za,Sjostrand:2007gs} and Delphes 3.4.1~\cite{deFavereau:2013fsa}.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.15\textwidth]{figures/panel_1.pdf}
\includegraphics[width=0.15\textwidth]{figures/panel_3.pdf}
\includegraphics[width=0.15\textwidth]{figures/panel_2.pdf}
\includegraphics[width=0.23\textwidth]{figures/NN_FGSM.pdf}
\includegraphics[width=0.23\textwidth]{figures/D2_FGSM.pdf}
\label{fig:FGSM}
\caption{Individual jet adversary.  The bottom right plot shows that we can't attack $D_2$ !}
\end{figure}
